Response to reviewers

### 2022-02-17 paper/paper.tex
working response

>>>>

\begin{verbatim}
#> # A tibble: 43 x 6
#>    id     year  wage age_1979 gender   exp
#>    <fct> <int> <dbl>    <int> <fct>  <dbl>
#>  1 1663   1987  5.90       15 MALE    4.26
#>  2 1663   1988  7          15 MALE    4.26
#>  3 1663   1989 14          15 MALE    4.26
#>  4 2466   1988  6.97       17 MALE    8.17
#>  5 2466   1989  6.97       17 MALE    8.17
#>  6 2466   1990  7.25       17 MALE    9.03
#>  7 2466   1991  7.25       17 MALE    9.03
#>  8 2594   1986 11          17 MALE    5.95
#>  9 2594   1987  9.68       17 MALE    5.95
#> 10 3087   1993 18.7        18 MALE   10.7 
#> # ... with 33 more rows
\end{verbatim}

### 2022-02-17 response/response1.Rmd
working response

@@

@@

@@

@@

@@

@@

* We use `MASS` package instead of `robustlmm` package. We have tried to use `robustlmm`, but perhaps because the data is large and imbalanced, the model was not converging. Also, for reproducibility reason, we made it more affordable (in terms of memory and time), especially when people want to perform the stages in cleaning the data in class/teaching.

@@

@@

@@

>>>>

* We have changed Fig 2 to show 36 individuals, that display the range of wages experience, including some with questionable values. The figure caption reflects this and more details are provide din the text.

@@

* This section has been re-written, and additional details provided.

@@

* Done

@@

* The abstract has been re-written to reflect the re-framing of the paper.

@@

* Paper has been re-written to change focus.

@@

* See explanation above

@@

* The `robustlmm` model would not converge. We have added some text to the paper on this.

@@

* **NEED HELP** We have added more explanation on the process used to decide on the threshold.

@@

* **NEED HELP** Figure 8 has been updated, and other comparisons of the original and refreshed data have been added. There are still some differences, but with the change in variables being created and better filtering to get the dropouts the data are now more similar.

@@

* NEED HELP We are really not sue what this refers to.
